A Switching Planner for Combined Task and Observation Planning

### 2011-02-03 subarchitectures/planner.sa/trunk/src/latex/AAAI11/relatex.tex
New intro text

Addressing task and observation planning specifically, there have been
a number of recent developments where the underlying problem is
modelled as a POMDP.
%%
For vision algorithm
selection,~\citeauthor{hippo-jnl}~(\citeyear{hippo-jnl}) exploit a
natural hierarchical decomposition of the underlying POMDP into
subproblems where decision-theoretic planning is reasonably
fast. \citeauthor{doshi08:pref_elic}~(\citeyear{doshi08:pref_elic})
represent a preference elicitation problem as a POMDP and take
advantage of symmetry in the belief space ---essentially the idea that
it does not matter what the value of the variable you are trying to
observe is--- to exponentially shrink the state space. Although we
have been actively exploring the \citeauthor{doshi08:pref_elic}
approach, those exploitable structures are not present in problems we
have considered so far due to the task planning requirement. 
%%
\citeauthor{kurniawati:etal:2010}~(\citeyear{kurniawati:etal:2010}) 
%%
Finally,
our approach is in a similar vein to the more classical {\em
dual-mode} control~\cite{cassandra96actingunder}, however in our case
entropy reduction is targeted by planning in an abstract process which
is informed by one execution trace ---computed by a {\em classical}
planner--- and the underlying belief-state.

More generally, there has been much recent work on scaling POMDP
solution procedures to medium-sized instances~\cite{shani:etal:08}. In
the case of general domain-independent factored systems, the
state-of-the-art scales to relatively small problems with $2^{22}$
states~\cite{shani:etal:2008}. At their limit, these procedures take
over an hour to converge, and $\sim10$ seconds on average to perform a
single Bellman backup.  For classes of POMDP that feature exploitable
structures (e.g., no actions with negative effects), problems with as
many as $10^{30}$ states can be targeted by offline
procedures~\cite{brunskill:russell:2010}. Moving someway towards
addressing real-time decision making, recent online POMDP solution
procedures have been developed which can exploit highly approximate
value functions -- typically computed using a point-based procedure --
and heuristics in forward search~\cite{ross:etal:2008}. Their
applicability in our setting is limited, firstly because they only
scale to smaller problems, with thousands of states, and also due to
the large amount of
\emph{problem-specific} offline processing that might be required to get useful
search guidance. A {\em very} recent and promising online approach for
large POMDPs employs Monte-Carlo sampling to break the curse of
dimensionality in situations where goal reachability is {\em easily}
determined~\cite{silver:veness:2010}.

>>>>

Addressing task and observation planning specifically, there have been
a number of recent developments where the underlying problem is
modelled as a POMDP.
%%
For vision algorithm
selection,~\citeauthor{hippo-jnl}~(\citeyear{hippo-jnl}) exploit a
natural hierarchical decomposition of the underlying POMDP into
subproblems where decision-theoretic planning is reasonably
fast. \citeauthor{doshi08:pref_elic}~(\citeyear{doshi08:pref_elic})
represent a preference elicitation problem as a POMDP and take
advantage of symmetry in the belief space ---essentially the idea that
it does not matter what the value of the variable you are trying to
observe is--- to exponentially shrink the state space. Although we
have been actively exploring the \citeauthor{doshi08:pref_elic}
approach, those exploitable structures are not present in problems we
have considered so far due to the task planning requirement. 
%%
%%
Finally,
our approach is in a similar vein to the more classical {\em
dual-mode} control~\cite{cassandra96actingunder}, however in our case
entropy reduction is targeted by planning in an abstract process which
is informed by one execution trace ---computed by a {\em classical}
planner--- and the underlying belief-state.

More generally, there has been much recent work on scaling POMDP
solution procedures to medium-sized instances~\cite{shani:etal:08}. In
that
setting \citeauthor{kurniawati:etal:2010}~(\citeyear{kurniawati:etal:2010})
recently addressed an inefficiency of offline point-based techniques
in problems with medium length planning horizons, however their
approach take tens of minutes to start yielding good behaviour even in
relatively small problems (tens of thousands of states). In the case
of general domain-independent factored systems, the state-of-the-art
scales to relatively small problems with $2^{22}$
states~\cite{shani:etal:2008}. At their limit, these procedures take
over an hour to converge, and $\sim10$ seconds on average to perform a
single Bellman backup.  For classes of POMDP that feature exploitable
structures (e.g., no actions with negative effects), problems with as
many as $10^{30}$ states can be targeted by offline
procedures~\cite{brunskill:russell:2010}. Moving someway towards
addressing real-time decision making, recent online POMDP solution
procedures have been developed which can exploit highly approximate
value functions -- typically computed using a point-based procedure --
and heuristics in forward search~\cite{ross:etal:2008}. Their
applicability in our setting is limited, firstly because they only
scale to smaller problems, with thousands of states, and also due to
the large amount of
\emph{problem-specific} offline processing that might be required to get useful
search guidance. A {\em very} recent and promising online approach for
large POMDPs employs Monte-Carlo sampling to break the curse of
dimensionality in situations where goal reachability is {\em easily}
determined~\cite{silver:veness:2010}.
